Distributions

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Change lims for gamma plot

```{r message=FALSE, warning=FALSE}
library(aracari)
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(fitdistrplus)
library(stringr)
library(gt)

@@

@@

@@

```{r FigureX, fig.height=12, fig.width=12}
library(MetBrewer)

colsx <- met.brewer("Gauguin", n = 7)
aval <- 0.3

@@

pp.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  figx.theme -> pp.gam

@@

np.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  figx.theme -> np.gam

@@

plot_grid(cp.grid, pp.grid, np.grid, nrow = 3)
```

>>>>

```{r message=FALSE, warning=FALSE}
library(aracari)
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(fitdistrplus)
library(stringr)
library(gt)
library(MetBrewer)
library(purrr)

@@

cp.best

@@

# What values to use
map_dbl(cp.best[,-c(1,2)], min, na.rm = TRUE)
map_dbl(cp.best[,-c(1,2)], max, na.rm = TRUE)
map_dbl(pp.best[,-c(1:3)], min, na.rm = TRUE)
map_dbl(pp.best[,-c(1:3)], max, na.rm = TRUE)
map_dbl(np.best[,c(4:8)], min, na.rm = TRUE)
map_dbl(np.best[,c(4:8)], max, na.rm = TRUE)

@@

```{r FigureX, fig.height=9, fig.width=9}

colsx <- met.brewer("Tiepolo", n = 7)
aval <- 0.3

@@

pp.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  lims(x = c(0, 0.23), y = c(0.4, 2.4)) +
  figx.theme -> pp.gam

@@

np.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  lims(x = c(0, 0.23), y = c(0.4, 2.4)) +
  figx.theme -> np.gam

@@

plot_grid(cp.grid, pp.grid, np.grid, nrow = 3)

ggsave2(filename = "Ch2_distributions/Figures/Figurex.png")
```
